An Empirical Analysis of the Role of Energy in Economic Growth

### 2015-01-08 Articles/Article_EnerEcon_2014/EconGrowth4.Rnw
Added more of Martin's comments.

In the context of linear models (regression), resamples are generally created
by residual resampling.  
In our case, we formed resamples by adding to the fitted 
response ($\hat{y}$) the product of a residual from the original model fit and 
random sign ($-1$ or $1$, each with probability $0.5$).  
For the case of Cobb-Douglas and LINEX models, 
this residual resampling occurs on the 
log-transformed data.

Intuitively, this method assumes that the residuals are indicative of 
the variability (from many potential sources) inherent in the data such that
it would be unsurprising if the residual from 
any particular year had been observed in a different year. 
Thus, a resampled response $\tilde Y'$ can be computed as 
**** Randy edit the following equations to reflect the fact that we're fitting in log space? --MKH ****
%
\begin{equation}
  \tilde Y_i' = \hat y_i \pm r_j
\end{equation}
%
where 
%
\begin{equation}
  r_i = y_i - \hat y_i
\end{equation}
%
both the sign ($\pm$) and the index of the residual 
($j$,~typically different from $i$) 
are chosen at random (with replacement). 
We repeated the resampling process 1000 times for each
combination of growth model and country, 
both with and without energy as appropriate.

>>>>

In the context of linear models (regression), resamples are generally created
by residual resampling.  
In our case, we formed resamples by adding to the fitted 
response ($\hat{y}$) the product of a residual from the original model fit and 
random sign ($-1$ or $1$, each with probability $0.5$).  
**** I have little idea what this means, 
and more importantly why we follow this particular approach :) 
(another way of saying as we are publishing 
in an economics journal with an audience limited in statistics, 
we must be very clear) --MdW ****
**** Randy: can you do a little more explaining here? 
Perhaps we should say that this is a standard way of forming the resample time series? --MKH ****
For the case of Cobb-Douglas and LINEX models, 
this residual resampling occurs on the 
log-transformed data.
Intuitively, this method assumes that the residuals are indicative of 
the variability (from many potential sources) inherent in the data such that
it would be unsurprising if the residual from 
any particular year had been observed in a different year. 
Thus, a resampled response $\tilde Y'$ can be computed as 
**** Randy edit the following equations to reflect the fact that we're fitting in log space? --MKH ****
%
\begin{equation}
  \tilde Y_i' = \hat y_i \pm r_j
\end{equation}
%
where 
%
\begin{equation}
  r_i = y_i - \hat y_i
\end{equation}
%
both the sign ($\pm$) and the index of the residual 
($j$,~typically different from $i$) 
are chosen at random (with replacement). 
We repeated the resampling process 1000 times for each
combination of growth model and country, 
both with and without energy as appropriate.
**** do we follow precedent here? or just a number we fell comfortable with? 
may warrant a reference and/or short explanation why we choose 1000 times. --MdW ****
**** Randy: Can you provide some additional explanation here? --MKH ****
